% \paragraph{} There is a wealth of theoretical and practical research, forming an essential background to the work presented here. To provide adequate grounding, we discuss a handful of the most notable --- split into two distinct fields, \textit{Information Flow Control} and Intel SGX. Little study has been conducted in this overlap, but that which exists will be highlighted as appropriate.


\section{\textit{Flume} and \textit{CamFlow}}

\paragraph{} Both \textit{Flume}~\cite{flume} and \textit{CamFlow}~\cite{camflow} present practical \acrshort{difc} systems for generic, \acrshort{os}-level protection in Linux. Their models are not dissimilar, with \textit{CamFlow} refining the basic \textit{Flume} approach. A detailed overview of the \textit{CamFlow} model has already been presented in ยง~\ref{sec:ifc}, but there are important differences in the implementation of the two works.

\paragraph{Flume} \textit{Flume} takes the form of a userspace reference monitor. Processes confined by Flume are not able to perform most \textit{syscalls} directly --- an \textit{interposition layer} replaces \textit{syscalls} with \acrfull{ipc} to the reference monitor, which enforces \acrshort{ifc} policies and ensuring operation safety on processes' behalf. The majority of complexity lies in the reference monitor, with its \acrshort{lsm} only a small auxiliary companion. The authors report a $30-40$\% overhead.

\paragraph{CamFlow} In contrast, the \textit{CamFlow} core \acrshort{ifc} implementation lies entirely within its \acrshort{lsm}, efficiently exploiting kernel functionality to minimise the overhead it creates. File operations in microbenchmark tests produce an 11\% average overhead.


\subsection{Other IFC Systems}
\paragraph{} Many different approaches to \acrshort{ifc} have been published; the most influential to this project will be briefly summarised.

\paragraph{} \textit{Asbestos} is a prototype \acrshort{os} by Efstathopoulos et al.~\cite{asbestos} that provides entity labelling and isolation as an \acrshort{os} primitive. Applications express individual policies via a custom kernel interface, and all dataflow is protected, including \acrshort{ipc} and system-wide information flows. Additionally, a novel event abstraction and sub-process \textit{security contexts} allows processes to act on behalf of multiple entities. \textit{HiStar} (Zeldovich et al.~\cite{10.5555/1298455.1298481}) builds on the \textit{Asbestos} model, minimising the size of the system's \acrshort{tcb} --- the system has no notion of \textit{superuser}, with no code other than the kernel being fully trusted. An important consequence of this is that the risk of data leaking via \textit{covert channels} is drastically reduced. \textit{DStar} (Zeldovich et al.~\cite{10.5555/1387589.1387610}) translates \textit{HiStar} into a distributed context, translating labels between \acrshort{ifc}-enabled hosts with the help of a globally-meaningful set of tags. In contrast, \textit{Aeolus} (Cheng et al.~\cite{10.5555/2342821.2342833}), derived from \textit{Asbestos}, deploys a common \acrshort{tcb} across all nodes in a distributed system to enforce \acrshort{ifc}; it filters \acrshort{io} and both inter- and intra- process communication.

\paragraph{} Laminar (Roy et al.~\cite{10.1145/1543135.1542484}) takes a similar approach to \textit{Flume}, using an \acrshort{lsm} for policy enforcement, but extends it with customisation to the \textit{\acrfull{jvm}}.~\cite{jvm} to support thread-level isolation and heap-object protection. This approach has proved powerful in applying \acrshort{difc} to popular processing systems such as \textit{MapReduce}~\cite{mapreduce} and \textit{Hadoop}.~\cite{hadoop}


\section{Interoperation between Linux and SGX} 
\paragraph{} The relationship between \acrshort{sgx} and Linux has at times been difficult; Intel has been attempting to upstream \textit{isgx}, the \acrshort{sgx} driver, into the mainline kernel for six years.\footnote{The \textit{linux-sgx} patch-set has seen $32^{\text{nd}}$ revisions; \url{https://lore.kernel.org/linux-sgx/}.} A source of extreme friction lies in the fact that enclaves are not operable in ring-0, forcing research seeking to use \acrshort{sgx} to harden the kernel itself to be creative integrating it.

\paragraph{} The \textit{TresorSGX}~\cite{10.1145/3007788.3007796} project was one of the first to consider the practicalities of this relationship seriously, constructing an externalised interface for kernel functionality to be offloaded to an enclave via a specialised kernel module. Mainly focusing on disk encryption, the prototype achieved its security goals but struggled with performance, only performing at 1\% the bandwidth of its kernel-embedded counterpart. The most prevalent performance hit came from kernel $\leftrightarrow$ enclave communication overhead, made worse by the need to exit and re-enter ring-0.


\paragraph{} Various other studies touch upon these issues, including:

\begin{itemize}
    \item \textit{Custos} (Paccagnella et al.~\cite{Karande2017SGXLogSS}); tamper-detection for audit logs using \acrshort{sgx}. The design attaches itself to the pre-existing Linux Audit Framework, deliberately avoiding execution tied to the kernel. Performance overheads are $2-7$\%. 
    \item \textit{DelegaTEE} (Matetic et al.~\cite{10.5555/3277203.3277308}); credential delegation between two computer systems by enforcing either centrally brokered or peer-to-peer. \textit{discretionary access control}. The system does not operate at the \acrshort{os}-layer, but presents an effective capability-sharing system for modified applications via an \acrshort{sgx} mediator.
    \item \textit{NeXUS} (Djoko et al.~\cite{nexus8809505}); practical access control for remote storage systems such as \textit{Google Drive}. The design uses a \textit{stackable} filesystem to interface with encrypted volumes --- \acrshort{sgx} is used to protect and share these encryption keys. Performance overheads are $100$\%.
\end{itemize}


\section{Dataflow Protection using SGX}
\paragraph{} Research into applying the protections afforded by \acrshort{sgx} to large-scale distributed computation accelerated recently --- the most prominent projects are detailed here. 

\begin{itemize}
    \item \textit{SCONE}~\cite{10.5555/3026877.3026930} presents a secure container framework for \textit{Docker}.~\cite{docker-security} Using a secured version of the standard library for C it transparently encrypts/decrypts \acrshort{io} crossing the container's boundary. The authors claim $\times 0.6-1.2$ the performance of native throughput.
    \item \textit{VC3}~\cite{vc37163017} secures \textit{Hadoop} \textit{MapReduce} computations --- the \textit{Hadoop} platform is not considered part of the \acrshort{tcb}, thus allowing the system's security invariants to remain unaffected if it were to be compromised. The reported performance overhead is 8\% (for full read/write integrity).
    \item The \textit{Maru} project~\cite{maru} added support for running distributed \textit{Apache Spark} in \acrshort{sgx} enclaves. Data residing outside of a worker in \textit{\acrshort{hdfs}} is sealed, removing the needs for the need for \textit{Hadoop} to be a part of the \acrshort{tcb}. A notably difficulty was porting the \textit{\acrshort{jvm}} to function efficiently inside an enclave; \acrshort{sgx} v1 restricts the \acrshort{epc} size to 128MB, severely penalising applications that struggle to run in relatively small memory footprints.
    \item \textit{Ryoan}~\cite{ryoan199358} provides a distributed sandbox environment to confine untrusted applications running on sensitive data in the cloud; a specific use case is computation outsourcing. It uses \textit{confining labels} to create a weakened form of \acrshort{ifc} tracking; processing nodes must be stateless and once tainted by a request cannot access resources outside the execution environment. Enforcement is managed both by \acrshort{sgx} and \textit{NaCl}~\cite{nacl} for the host application. 
\end{itemize}

